Backpropagating Gravitational wave events

### 2022-03-17 src/ms.tex
Add m1 m2 alpha figure. I don't think we need the CE vs SMT figure here
typo fixing

Indeed, one of the most common skepticism population synthesis studies receives is a simulations set usually only cover a small subdomain of the entire parameter space,
i.e. only vary a number of hyper-parameters while holding all others fixed to some "default" values.
Even with recently development on using emulators to speed up the simulation process, training the emulators also require a decent amount of samples in the parameter space of interest.
For example, say we want to emulate a model with 10 parameters, this simplest option for constructing a bank of simulations for training is to lay down a grid. Along each axis we put the barely minimum of $2$ simulations, this would still require $1024$ simulations.
The fastest kind of population synthesis simulation takes about an hour to complete, where longer simulations could take days.
This means even training an emulator is impossible in high dimensional space.

@@

\begin{figure*}
\includegraphics[width=0.98\textwidth]{static/GW150914_corner.pdf}
\caption{The posterior for GW150914 in both the progenitor parameter space and hyper-parameter space.
$M_1$ and $M_2$ are the progenitors' masses. $\log{t_{orb}}, e, \log{Z}$ are the progenitor binary's log orbital period, eccentricity and log metallicity at ZAMS.
$\alpha$ is the common envelope efficiency.
$f_{\rm acc}$ is the fraction of mass accreted during stable mass transfer.
$q_{\rm crit 3,4}$ are the ciritical mass during \kw{Katie fill in},
$\sigma$ is the mean magnitude of the Maxwellian distribution characterizing natal kick strength.
}
\label{fig:GW150914_posterior}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=0.49\textwidth]{static/GW150914_CE_SMT.pdf}
\caption{}
\label{fig:GW150914_CE_SMT}
\end{figure}
\kw{Add figure of stable mass transfer vs common envelope}

\begin{figure}
\caption{}
\label{fig:GW150914_M1_M2_q3}
\end{figure}

>>>>

Indeed, one of the most common skepticism population synthesis studies receives is a simulation set usually only cover a small subdomain of the entire parameter space,
i.e. only vary a number of hyper-parameters while holding all others fixed to some "default" values.
Even with recently development on using emulators to speed up the simulation process, training the emulators also require a decent amount of samples in the parameter space of interest.
For example, say we want to emulate a model with 10 parameters, this simplest option for constructing a bank of simulations for training is to lay down a grid. Along each axis we put the barely minimum of $2$ simulations, this would still require $1024$ simulations.
The fastest kind of population synthesis simulation takes about an hour to complete, where longer simulations could take days.
This means even training an emulator is impossible in high dimensional space.

@@

\begin{figure*}
\includegraphics[width=0.98\textwidth]{static/GW150914_corner.pdf}
\caption{The posterior for GW150914 in both the progenitor parameter space and hyper-parameter space.
$M_1$ and $M_2$ are the progenitors' masses. $\log{t_{orb}}, e, \log{Z}$ are the progenitor binary's log orbital period, eccentricity and log metallicity at ZAMS.
$\alpha$ is the common envelope efficiency.
$f_{\rm acc}$ is the fraction of mass accreted during stable mass transfer.
$q_{\rm crit 3,4}$ are the cirtical mass during \kw{Katie fill in},
$\sigma$ is the mean magnitude of the Maxwellian distribution characterizing natal kick strength.
}
\label{fig:GW150914_posterior}
\end{figure*}

@@

% \begin{figure}
% \includegraphics[width=0.49\textwidth]{static/GW150914_CE_SMT.pdf}
% \caption{}
% \label{fig:GW150914_CE_SMT}
% \end{figure}
% \kw{Add figure of stable mass transfer vs common envelope}

\begin{figure}
\includegraphics[width=0.49\textwidth]{static/GW150914_m1m2alpha.png}
\caption{}
\label{fig:GW150914_M1_M2_q3}
\end{figure}
